\textbf{Evidence for a Change to Aerosol Fractions: In a Gobi Town}

### 2024-11-25 submission/Outline_20241121.Rmd
outline -  abstract, justify

## Abstract (150 words)
Driven by mining industrial progress, household coal combustion has increased greatly in Mongolia since the 2000s. Demographic evidence has revealed an ongoing reduction in rural-nomadic lifestyle and a rise of the population at urban areas, which may gradually extend a household major source of fine particulate matter (PM2.5) air pollution in winter as a heating. Together with observations that lifespan in various animal species is flexible and can be increased by genetic or pharmaceutical intervention, these results have led to suggestions that longevity may not be subject to strict, species-specific genetic constraints. Here, by analysing global demographic data, we show that improvements in survival with age tend to decline after age 100, and that the age at death of the world’s oldest person has not increased since the 1990s. Our results strongly suggest that the maximum lifespan of humans is fixed and subject to natural constraints.
Storyline:

>>>>

## Abstract (150 words)
Driven by mining industrial progress, household coal combustion has increased greatly in Mongolia since the 2000s. Demographic evidence has revealed an ongoing reduction in rural-nomadic lifestyle and a rise of the population at urban areas, which may gradually extend a household winter heating as a major source of fine particulate matter (PM2.5). Together ff with observations that lifespan in various animal species is flexible and can be increased by genetic or pharmaceutical intervention, these results have led to suggestions that longevity may not be subject to strict, species-specific genetic constraints. Here, by analysing global demographic data, we show that improvements in survival with age tend to decline after age 100, and that the age at death of the world’s oldest person has not increased since the 1990s. Our results strongly suggest that the maximum lifespan of humans is fixed and subject to natural constraints.
Storyline:

### 2024-11-25 submission/Outline_20241121.tex
outline -  abstract, justify

Driven by mining industrial progress, household coal combustion has
increased greatly in Mongolia since the 2000s. Demographic evidence has
revealed an ongoing reduction in rural-nomadic lifestyle and a rise of
the population at urban areas, which may gradually extend a household
major source of fine particulate matter (PM2.5) air pollution in winter
as a heating. Together with observations that lifespan in various animal
species is flexible and can be increased by genetic or pharmaceutical
intervention, these results have led to suggestions that longevity may
not be subject to strict, species-specific genetic constraints. Here, by
analysing global demographic data, we show that improvements in survival
with age tend to decline after age 100, and that the age at death of the
world's oldest person has not increased since the 1990s. Our results
strongly suggest that the maximum lifespan of humans is fixed and
subject to natural constraints. Storyline:

>>>>

Driven by mining industrial progress, household coal combustion has
increased greatly in Mongolia since the 2000s. Demographic evidence has
revealed an ongoing reduction in rural-nomadic lifestyle and a rise of
the population at urban areas, which may gradually extend a household
winter heating as a major source of fine particulate matter (PM2.5).
Together ff with observations that lifespan in various animal species is
flexible and can be increased by genetic or pharmaceutical intervention,
these results have led to suggestions that longevity may not be subject
to strict, species-specific genetic constraints. Here, by analysing
global demographic data, we show that improvements in survival with age
tend to decline after age 100, and that the age at death of the world's
oldest person has not increased since the 1990s. Our results strongly
suggest that the maximum lifespan of humans is fixed and subject to
natural constraints. Storyline:
